\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2021

% ready for submission
\usepackage[final]{neurips_2021}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2021}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2021}

% to avoid loading the natbib package, add option nonatbib:
%    \usepackage[nonatbib]{neurips_2021}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage[mathscr]{euscript}
\usepackage{graphicx}
\title{Machine Learning, 2023 Spring\\Assignment 3}
% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.



\begin{document}

\maketitle

\begin{abstract}

\end{abstract}





\textcolor{blue}{Requirement}
Provide a numerical experiment for SGD algorithm, and submit the results in a report. Both code and report need to be submit.
Contents of the report: 
\begin{enumerate}
    \item Background: Introduce the purpose, background of the experiment.
    \item Data acquisition: How the data is generated.
    \item Algorithm: The optimization model and the applied alogrithm, especially the alogrithm parameters.
    \item Experiment result for the following taskes:
    \begin{enumerate}
        \item SGD with fixed step length. (At least 3 different step length.)
        \item SGD with decresing step length.
        \item Demonstrate early termination. (If the result is not perfect, please demonstrate it in discussion.)
        \item (optional) Compare GD and SGD under large dataset.
    \end{enumerate}
    
\end{enumerate}


\textbf{Tips}

    (a) The programing language is not restricted.(Python / Matlab)

    (b) The optimization model should be suitable for GD/SGD algorithm. e.g. Logistic regression / Least square with about 10 variable.

    (c) Choose enough training data $N$.$N$ should be no less than $10^3$. You can also approximate the distribution, and out of sample error with more data generated.
    (First genreate $\approx 10*N $ data points, to approximate the distribution, and sample $N$ training data in it. The out of sample error can also be evluated with the approximate distribution.) 

\end{document}